\textsf{Are large language models superhuman chemists?}

### 2024-03-21 src/tex/ms.tex
parallel coordinates and updated plot

% Radar chart
To obtain a more detailed understanding of the performance of the models, we also analyzed the performance of the models in different subfields of the chemical sciences.
For this analysis, we defined a set of topics (see \Cref{sec:meth-topic}) and classified the questions into these topics based and hand-crafted rules as well as classifier models.
We then computed the percentage of questions that the models, or humans, answered completely correctly for each topic.

@@

% Calculation vs. no calculation
Given that some of the questions in \chembench require elaborate calculations, we also analyzed if the models perform differently on those questions.
For this, we manually annotated the questions that require calculations and performed the analysis on only those questions.

% Estimate of difficulty
One might wonder whether the models are capable of estimating if they will be able to answer a question correctly. 
If they were able to do so, incorrect answers would be less problematic as one would be able to detect when an answer is incorrect.
To investigate this, we prompted\autocite{xiong2023llms} some of the top-performing models to estimate the on an ordinal scale their confidence in their ability to answer the question correctly.

@@

Our findings also highlight the nuanced tradeoff between breadth and depth of evaluation frameworks. % link to the missing correlation

>>>>

% Radar chart
\paragraph{Performance per topic} To obtain a more detailed understanding of the performance of the models, we also analyzed the performance of the models in different subfields of the chemical sciences.
For this analysis, we defined a set of topics (see \Cref{sec:meth-topic}) and classified the questions into these topics based and hand-crafted rules as well as classifier models.
We then computed the percentage of questions that the models, or humans, answered completely correctly for each topic.

@@

% Calculation vs. no calculation
Given that some of the questions in \chembench require elaborate calculations, we also analyzed if the models perform differently on those questions.
For this, we manually annotated the questions that require calculations and performed the analysis on only those questions.  % TODO add some analysis here

% Estimate of difficulty
\paragraph{Confidence estimates} One might wonder whether the models are capable of estimating if they will be able to answer a question correctly. 
If they were able to do so, incorrect answers would be less problematic as one would be able to detect when an answer is incorrect.
To investigate this, we prompted\autocite{xiong2023llms} some of the top-performing models to estimate the on an ordinal scale their confidence in their ability to answer the question correctly.

@@

Our findings also highlight the nuanced tradeoff between breadth and depth of evaluation frameworks. % link to the missing correlation 
% also need for better ways of how humans actually use LLMs. How do they get the confidence?  
% an LLM is not a chemist and at least the current systems seem to be far from reasoning like a chemist 
% for fact like questions, that requires knowledge they might have seen on the internet, they work well, but for reasoning they are not good yet.
